\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Add titles to captions for connection box plots

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
Participants in E2 and E3 took a long time to connect.
The ``DNF'' (did not finish) shows how many did not connect.}
\label{fig:time_to_success_clamped}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Configuration times are much shorter than connection times, which means that most of the time was spent waiting for the connection to establish or time out. Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
Connection times.
Participants in E2 and E3 took a long time to connect.
The ``DNF'' (did not finish) shows how many did not connect.}
\label{fig:time_to_success_clamped}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Configuration times (connection time with time on progress screen subtracted).
The differences from Figure \ref{fig:time_to_success_clamped} (connection times) show that most of the time was spent waiting for the connection to establish or time out.
%Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
}
\label{fig:time_to_success_active_clamped}
\end{figure}
